Out-of-Sample Comparisons of Overfit Models

### 2017-04-21 floats/empirics-oos-mse-2b.tex
Add TeX files with simulation and empirical results to repo
I've decided to add _a few_ generated files to the main repository to
make my life easier; namely any graphics or tables that are included
in the main paper.

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] (248.66, 64.79) --
	(254.84, 71.45) --
	(261.02, 68.74) --
	(267.20, 66.28) --
	(273.38, 63.80) --
	(279.57,105.64) --
	(285.75,104.73) --
	(291.93,113.66) --
	(298.11,116.70) --
	(304.29,115.54) --
	(310.47,113.47) --
	(316.65,120.29) --
	(322.83,121.13) --
	(329.01,119.16) --
	(335.19,121.19) --
	(341.37,120.79) --
	(347.55,121.75) --
	(353.73,120.97) --
	(359.91,125.03) --
	(366.09,124.93) --
	(372.27,120.92) --
	(378.45,115.37) --
	(384.63,110.14);

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] (248.66, 67.69) --
	(254.84, 74.06) --
	(261.02, 71.45) --
	(267.20, 69.09) --
	(273.38, 66.79) --
	(279.57,107.26) --
	(285.75,106.40) --
	(291.93,115.08) --
	(298.11,118.01) --
	(304.29,116.97) --
	(310.47,115.08) --
	(316.65,121.60) --
	(322.83,122.36) --
	(329.01,120.66) --
	(335.19,122.70) --
	(341.37,122.44) --
	(347.55,123.48) --
	(353.73,122.73) --
	(359.91,126.40) --
	(366.09,126.32) --
	(372.27,122.61) --
	(378.45,117.59) --
	(384.63,112.83);

@@

\path[fill=fillColor] (248.66,128.74) --
	(248.66, 64.79) --
	(254.84, 71.45) --
	(261.02, 68.74) --
	(267.20, 66.28) --
	(273.38, 63.80) --
	(279.57,105.64) --
	(285.75,104.73) --
	(291.93,113.66) --
	(298.11,116.70) --
	(304.29,115.54) --
	(310.47,113.47) --
	(316.65,120.29) --
	(322.83,121.13) --
	(329.01,119.16) --
	(335.19,121.19) --
	(341.37,120.79) --
	(347.55,121.75) --
	(353.73,120.97) --
	(359.91,125.03) --
	(366.09,124.93) --
	(372.27,120.92) --
	(378.45,115.37) --
	(384.63,110.14) --
	(384.63,128.74) --
	cycle;
\definecolor[named]{drawColor}{rgb}{0.75,0.75,0.75}

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (248.66, 67.69) --
	(254.84, 74.06) --
	(261.02, 71.45) --
	(267.20, 69.09) --
	(273.38, 66.79) --
	(279.57,107.26) --
	(285.75,106.40) --
	(291.93,115.08) --
	(298.11,118.01) --
	(304.29,116.97) --
	(310.47,115.08) --
	(316.65,121.60) --
	(322.83,122.36) --
	(329.01,120.66) --
	(335.19,122.70) --
	(341.37,122.44) --
	(347.55,123.48) --
	(353.73,122.73) --
	(359.91,126.40) --
	(366.09,126.32) --
	(372.27,122.61) --
	(378.45,117.59) --
	(384.63,112.83);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (397.48,144.54);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40, 77.95) -- ( 50.40,128.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40, 77.95) -- ( 44.40, 77.95);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40, 90.65) -- ( 44.40, 90.65);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40,103.34) -- ( 44.40,103.34);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40,116.04) -- ( 44.40,116.04);

@@

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 38.40, 75.19) {-.10};

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 38.40,100.59) {-0.5};

>>>>

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] (248.66,124.54) --
	(254.84,125.33) --
	(261.02,125.15) --
	(267.20,123.84) --
	(273.38,123.35) --
	(279.57,120.81) --
	(285.75,124.16) --
	(291.93,124.28) --
	(298.11,123.31) --
	(304.29,123.14) --
	(310.47,122.78) --
	(316.65,123.16) --
	(322.83,120.87) --
	(329.01,122.51) --
	(335.19,123.70) --
	(341.37,123.48) --
	(347.55,123.46) --
	(353.73,122.23) --
	(359.91,123.13) --
	(366.09,120.07) --
	(372.27,106.08) --
	(378.45, 84.32) --
	(384.63, 63.80);

\path[draw=drawColor,line width= 0.3pt,line join=round,line cap=round] (248.66,125.42) --
	(254.84,126.24) --
	(261.02,126.11) --
	(267.20,124.81) --
	(273.38,124.31) --
	(279.57,122.08) --
	(285.75,125.43) --
	(291.93,125.60) --
	(298.11,124.74) --
	(304.29,124.74) --
	(310.47,124.48) --
	(316.65,124.85) --
	(322.83,122.60) --
	(329.01,124.53) --
	(335.19,125.81) --
	(341.37,125.79) --
	(347.55,125.98) --
	(353.73,125.02) --
	(359.91,125.98) --
	(366.09,123.38) --
	(372.27,111.40) --
	(378.45, 91.89) --
	(384.63, 73.27);

@@

\path[fill=fillColor] (248.66,128.74) --
	(248.66,124.54) --
	(254.84,125.33) --
	(261.02,125.15) --
	(267.20,123.84) --
	(273.38,123.35) --
	(279.57,120.81) --
	(285.75,124.16) --
	(291.93,124.28) --
	(298.11,123.31) --
	(304.29,123.14) --
	(310.47,122.78) --
	(316.65,123.16) --
	(322.83,120.87) --
	(329.01,122.51) --
	(335.19,123.70) --
	(341.37,123.48) --
	(347.55,123.46) --
	(353.73,122.23) --
	(359.91,123.13) --
	(366.09,120.07) --
	(372.27,106.08) --
	(378.45, 84.32) --
	(384.63, 63.80) --
	(384.63,128.74) --
	cycle;
\definecolor[named]{drawColor}{rgb}{0.75,0.75,0.75}

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (248.66,125.42) --
	(254.84,126.24) --
	(261.02,126.11) --
	(267.20,124.81) --
	(273.38,124.31) --
	(279.57,122.08) --
	(285.75,125.43) --
	(291.93,125.60) --
	(298.11,124.74) --
	(304.29,124.74) --
	(310.47,124.48) --
	(316.65,124.85) --
	(322.83,122.60) --
	(329.01,124.53) --
	(335.19,125.81) --
	(341.37,125.79) --
	(347.55,125.98) --
	(353.73,125.02) --
	(359.91,125.98) --
	(366.09,123.38) --
	(372.27,111.40) --
	(378.45, 91.89) --
	(384.63, 73.27);
\end{scope}
\begin{scope}
\path[clip] (  0.00,  0.00) rectangle (397.48,144.54);
\definecolor[named]{drawColor}{rgb}{0.00,0.00,0.00}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40, 68.44) -- ( 50.40,128.74);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40, 68.44) -- ( 44.40, 68.44);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40, 83.51) -- ( 44.40, 83.51);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40, 98.59) -- ( 44.40, 98.59);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 50.40,113.67) -- ( 44.40,113.67);

@@

\node[text=drawColor,anchor=base east,inner sep=0pt, outer sep=0pt, scale=  0.80] at ( 38.40, 65.68) {-.03};
